How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-07-27 paper.tex
a little more text and a ref

>>>>

The next step in the process is to actually communicate your issue with the
developers, generally in the form of a bug report.  Doing so effectively
requires striving for two somewhat contradictory goals: you must give the
developer all of the relevant information about the problem, as concisely as
possible.

The reason these two tasks are complicated is that, as a user, you often don't know what information is relevant.

rubber duck debugging \cite{Thomas-1999}-- the process of writing a good bug
report is analogous to solving the problem. Often, you can't really do it,
because if you knew what was necessary, you'd be able to solve your problem.
